InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

In fig. \ref{fig:gpt2} the text processors can be seen. The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one. It is visible that the double-whitespace processor alone has little effect whereas in combination with the typo one the result rise enourmously. This is due to the typo processor, since it alone also achieve great results. Here is also one evaluator, which produces only a black bar. 
Pretty much the exact same results can be seen in fig. \ref{fig:falcon} where radar has just black bars and typo as well as its combination with the roberta base evaluator achieve great results. The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.

>>>>

In fig. \ref{fig:gpt2} the text processors can be seen. The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one. It is visible that the double-whitespace processor alone has little effect whereas in combination with the typo one the result rise enourmously. This is due to the typo processor, since it alone also achieve great results. Here is also one evaluator, which produces only a black bar. 
Similar results can be seen in fig. \ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results. The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
